---
title: "Case Study"
author: "Nandini M"
date: "2023-10-10"
output: html_document
---

Load library and dataset
```{r}
library(p8105.datasets)
library(tidyverse)
library(ggplot2)
library(ggridges)
library(leaflet)

data(nyc_airbnb)

nyc_airbnb =
  nyc_airbnb |> 
  rename(borough = neighbourhood_group) |>
  mutate(stars = review_scores_location/2)

view(nyc_airbnb)
```

##Brainstorm questions

* Where are AirBNBs expensive?
  * Borough? Neighborhood?
  * Do other factors (room type) affect price? What about rating?
* How long are AirBNBs active?
  * Are AirBNBs illegal and do they get shut down?
* Which units have the most availability?
* How is review score impacted by location?
* How many apartments are run by one host?
  * Does that affect price?
  * Does that vary by neighborhood?
* Where are AirBNBs?
  * Borough? Neighborhood?
  * Lat and long?
  
## Attempt solutions

```{r}
nyc_airbnb |> 
  count(borough)
```

AirBNBs predominately located in Brooklyn and Manhattan

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)
  
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot()

nyc_airbnb |> 
  filter(price < 1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges() 
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

Try something else entirely.

```{r}
nyc_airbnb |> 
  filter(price < 1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat,~long, radius = .5)
```

